Cross-culture differences in tourists faced with Japanese hospitality: A text mining and natural language processing study of satisfaction and dissatisfaction factors in Chinese and Western cultures

### 2020-09-28 1_manuscript/itt-emotion.tex
Add: disc:implications

    \begin{figure}[h]
        \centering
        \begin{subfigure}[b]{0.45\textwidth}
            \includegraphics[width=\textwidth]{price_range_distribution_50_even_bins.png}
            \caption{50 equal lenght bins}
        \end{subfigure}
        \begin{subfigure}[b]{0.45\textwidth}
            \includegraphics[width=\textwidth]{price_range_distribution_bins_ver_2.png}
            \caption{manually set 9 price ranges}
        \end{subfigure}
    \caption{Price for one night distribution, blue: lowest price, orange: highest price.}
    \label{fig:price_dist}
    \end{figure}

@@

    \begin{figure}[h]
    \centering
    \includegraphics[width=0.6\textwidth]{depparse.png}
    \caption{Example of dependency parsing.}
    \label{fig:depparse}
    \end{figure}

@@

    \begin{figure}[h]
    \centering
    \includegraphics[width=0.6\textwidth]{postag.png}
    \caption{Example of POS tagging with the Penn Treebank tags.}
    \label{fig:postag}
    \end{figure}

@@

    \begin{table}[]

@@

  % Please add the following required packages to your document preamble:
  % \usepackage{multirow}
  % \usepackage{graphicx}
  \begin{table}[]
    \centering
    \caption{Determination of hard and soft attributes for Chinese keywords. }
    \label{tab:zh_hard_soft_keywords}
    \resizebox{0.7\textwidth}{!}{%
    \begin{tabular}{|c|l|l|}
      \hline
      \textbf{Keyword Emotion}                     & \multicolumn{1}{c|}{\textbf{Keyword}} & \multicolumn{1}{c|}{\textbf{Attribute Category}} \\ \hline
      \multirow{19}{*}{\textbf{Positive Keywords}} & \begin{CJK}{UTF8}{gbsn}不错\end{CJK}    & 50\% hard, 25\% soft, 25\% undefined             \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}大\end{CJK}   & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}干净\end{CJK}  & 25\% hard, 75\% soft                 \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK}  & 100\% soft                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}交通\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}棒\end{CJK}   & 25\% hard, 50\% soft, 25\% undefined \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}近\end{CJK}   & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}购物\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}环境\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}卫生\end{CJK}  & 100\% soft                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}新\end{CJK}   & 50\% hard, 25\% soft, 25\% undefined \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK}  & 100\% undefined                      \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}选择\end{CJK}  & 100\% undefined                      \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}地铁站\end{CJK} & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}远\end{CJK}   & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}附近\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}周边\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}赞\end{CJK}   & 100\% undefined                      \\ \hline
      \multirow{8}{*}{\textbf{Negative Keywords}}  & \begin{CJK}{UTF8}{gbsn}价格\end{CJK}    & 100\% soft                                       \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}一般\end{CJK}  & 50\% hard, 50\% soft                 \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}中文\end{CJK}  & 100\% soft                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}距离\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}地理\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}老\end{CJK}   & 75\% hard, 25\% soft                 \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}华人\end{CJK}  & 100\% soft                           \\ \hline
      \end{tabular}%
      }
  \end{table}

  \begin{figure}[h]
      \centering
      \begin{subfigure}[b]{0.45\textwidth}
          \includegraphics[width=\textwidth]{hard_soft_attr_zh_pos.png}
          \caption{Positive keywords}
      \end{subfigure}
      \begin{subfigure}[b]{0.45\textwidth}
          \includegraphics[width=\textwidth]{hard_soft_attr_zh_neg.png}
          \caption{Negative keywords}
      \end{subfigure}
  \caption{Hard and soft attributes from the top Chinese keywords for all price ranges}
  \label{fig:hard_soft_zh}
  \end{figure}

@@

  \begin{figure}[h]
      \centering
      \begin{subfigure}[b]{0.45\textwidth}
          \includegraphics[width=\textwidth]{hard_soft_attr_en_pos.png}
          \caption{Positive keywords}
      \end{subfigure}
      \begin{subfigure}[b]{0.45\textwidth}
          \includegraphics[width=\textwidth]{hard_soft_attr_en_neg.png}
          \caption{Negative keywords}
      \end{subfigure}
  \caption{Hard and soft attributes from the top English keywords for all price ranges}
  \label{fig:hard_soft_en}
  \end{figure}

@@

  % \subsection{Implications for hotel managers}\label{disc:implications}

    % Our study presents two important conclusions: one about hospitality and cultural differences, and another about managerial decisions towards two different populations. Chinese tourists are not experiencing the best that \textit{Omotenashi} has to offer. Either they do not get much satisfaction from hospitality or feel that basic language and communication needs are not being met. On the other hand, Western tourists are elated with Japanese hospitality. The other conclusion is that managerial decisions will mostly benefit Western tourists, except that Chinese language improvements and breakfast inclusion can satisfy more Chinese customers. Japan is recently seeing an increase in Chinese students as well as Western students of universities. Hiring students as part-time workers could increase the language services of a hotel.

    % To satisfy both customer types, hotel managers need to invest in cleanliness, deodorizing, and making hotel rooms tobacco-free. It could also be recommended to invest in breakfast inclusion and multilingual services and staff preparedness to deal with Chinese and English speakers. Western tourists were also observed to have high standards in comfort, which can be improved upon managerially for better reviews. Perhaps it could be suggested to perform surveys of the bedding that is most comfortable for Western tourists. However, not all hotels can invest in all of these factors simultaneously. Our results suggest that satisfying cleanliness needs can satisfy both customer types and that a low-cost investment could be to make the facilities tobacco-free.

    % Environmental factors, while not manageable after a hotel has finished its construction, are essential to consider for managers as well. As previously stated, transport systems and nearby shops are points of interest for both Chinese and Western tourists. Japanese hotel managers have to consider the location and surroundings since before the hotel is constructed. A suggestion could be to purchase land and start the construction after plans to make new subway lines are made.

    % It is left to the managers to consider their business model for the next strategy. One option could be attracting more Chinese customers in number with their observed low budgeting. Another could be attracting more high budget Western customers is on par with their business model. For example, investing more on cleanliness could improve on Western customers looking for high-quality lodging, even though the price per night would increase.

>>>>

    \begin{figure}[ht]
        \centering
        \begin{subfigure}[b]{0.45\textwidth}
            \includegraphics[width=\textwidth]{price_range_distribution_50_even_bins.png}
            \caption{50 equal lenght bins}
        \end{subfigure}
        \begin{subfigure}[b]{0.45\textwidth}
            \includegraphics[width=\textwidth]{price_range_distribution_bins_ver_2.png}
            \caption{manually set 9 price ranges}
        \end{subfigure}
    \caption{Price for one night distribution, blue: lowest price, orange: highest price.}
    \label{fig:price_dist}
    \end{figure}

@@

    \begin{figure}[ht]
    \centering
    \includegraphics[width=0.6\textwidth]{depparse.png}
    \caption{Example of dependency parsing.}
    \label{fig:depparse}
    \end{figure}

@@

    \begin{figure}[ht]
    \centering
    \includegraphics[width=0.6\textwidth]{postag.png}
    \caption{Example of POS tagging with the Penn Treebank tags.}
    \label{fig:postag}
    \end{figure}

@@

@@

  % Please add the following required packages to your document preamble:
  % \usepackage{multirow}
  % \usepackage{graphicx}
  \begin{table}[ht]
    \centering
    \caption{Determination of hard and soft attributes for Chinese keywords. }
    \label{tab:zh_hard_soft_keywords}
    \resizebox{0.7\textwidth}{!}{%
    \begin{tabular}{|c|l|l|}
      \hline
      \textbf{Keyword Emotion}                     & \multicolumn{1}{c|}{\textbf{Keyword}} & \multicolumn{1}{c|}{\textbf{Attribute Category}} \\ \hline
      \multirow{19}{*}{\textbf{Positive Keywords}} & \begin{CJK}{UTF8}{gbsn}不错\end{CJK}    & 50\% hard, 25\% soft, 25\% undefined             \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}大\end{CJK}   & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}干净\end{CJK}  & 25\% hard, 75\% soft                 \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK}  & 100\% soft                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}交通\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}棒\end{CJK}   & 25\% hard, 50\% soft, 25\% undefined \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}近\end{CJK}   & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}购物\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}环境\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}卫生\end{CJK}  & 100\% soft                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}新\end{CJK}   & 50\% hard, 25\% soft, 25\% undefined \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK}  & 100\% undefined                      \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}选择\end{CJK}  & 100\% undefined                      \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}地铁站\end{CJK} & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}远\end{CJK}   & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}附近\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}周边\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}赞\end{CJK}   & 100\% undefined                      \\ \hline
      \multirow{8}{*}{\textbf{Negative Keywords}}  & \begin{CJK}{UTF8}{gbsn}价格\end{CJK}    & 100\% soft                                       \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}一般\end{CJK}  & 50\% hard, 50\% soft                 \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}中文\end{CJK}  & 100\% soft                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}距离\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}地理\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}老\end{CJK}   & 75\% hard, 25\% soft                 \\ \cline{2-3} 
       & \begin{CJK}{UTF8}{gbsn}华人\end{CJK}  & 100\% soft                           \\ \hline
      \end{tabular}%
      }
  \end{table}

  \begin{figure}[ht]
      \centering
      \begin{subfigure}[b]{0.45\textwidth}
          \includegraphics[width=\textwidth]{hard_soft_attr_zh_pos.png}
          \caption{Positive keywords}
      \end{subfigure}
      \begin{subfigure}[b]{0.45\textwidth}
          \includegraphics[width=\textwidth]{hard_soft_attr_zh_neg.png}
          \caption{Negative keywords}
      \end{subfigure}
  \caption{Hard and soft attributes from the top Chinese keywords for all price ranges}
  \label{fig:hard_soft_zh}
  \end{figure}

@@

  \begin{figure}[ht]
      \centering
      \begin{subfigure}[b]{0.45\textwidth}
          \includegraphics[width=\textwidth]{hard_soft_attr_en_pos.png}
          \caption{Positive keywords}
      \end{subfigure}
      \begin{subfigure}[b]{0.45\textwidth}
          \includegraphics[width=\textwidth]{hard_soft_attr_en_neg.png}
          \caption{Negative keywords}
      \end{subfigure}
  \caption{Hard and soft attributes from the top English keywords for all price ranges}
  \label{fig:hard_soft_en}
  \end{figure}

@@

  \subsection{Price range differences}\label{disc:price}

    % some big paragraph about changing the way they speak, and about expectations, nice surprise, etc. 
    % Introduce the concept of logical expectations vs feelings expectations.
    % For example expecting it to be clean: ok just as expected / what?! it's not clean?! / cigarette
    %             expecting them to be nice: Still feel happy after they were nice
    % Omotenashi comes in play here.

    % paragraph about differences in perceptions from each culture
    %

    % paragraph about things that stay the same across all prices

    %

  \subsection{Implications for hotel managers}\label{disc:implications}

    Our study presents two important conclusions: one about hospitality and cultural differences, and another about managerial decisions towards two different populations. Chinese tourists, as a whole, are not showing the most satisfaction towards \textit{omotenashi}, instead focusing on the hard attributes of a hotel. Either they do not get as much satisfaction from hospitality as Western tourists, or feel that basic language and communication needs are not being met, so they receive a lesser impression. On the other hand, Western tourists are elated with Japanese hospitality, preferring soft attributes that management can influence to hard set ones. The other conclusion is that managerial decisions will mostly benefit Western tourists, excepting that Chinese language improvements and breakfast inclusion can satisfy more Chinese customers. Japan is recently seeing an increase in Chinese students as well as Western students of universities. Hiring students as part-time workers could increase the language services of a hotel.

    To satisfy both customer types, hotel managers need to invest in cleanliness, deodorizing, and making hotel rooms tobacco-free. It could also be recommended to invest in breakfast inclusion and multilingual services and staff preparedness to deal with Chinese and English speakers. Western tourists were also observed to have high standards in comfort, which can be improved upon managerially for better reviews. Perhaps it could be suggested to perform surveys of the bedding that is most comfortable for Western tourists. However, not all hotels can invest in all of these factors simultaneously. Our results suggest that satisfying cleanliness needs can satisfy both customer types and that a low-cost investment could be to make the facilities tobacco-free. Our results are also divided by price ranges, so a hotel manager can consider which analysis suits their hotel the most.

    Hard attributes, while not manageable after a hotel has finished its construction, are essential to consider for managers as well. As previously stated, transport systems and nearby shops are points of interest for both Chinese and Western tourists. Japanese hotel managers have to consider the location and surroundings since before the hotel is constructed. A suggestion could be to purchase land and start the construction after plans to make new subway lines are made.

    It is left to the managers to consider their business model for the next strategy. One option could be attracting more Chinese customers in number with their observed low budgeting. Another could be attracting more high budget Western customers is on par with their business model. For example, investing more on cleanliness could improve on Western customers looking for high-quality lodging, even though the price per night would increase. On the other hand, hotels might be considered costly by Chinese customers wherever such an investment is made.
